---
title: "PTB1 Practice 1 — 30 Debugging Exercises"
author: "__"
output: html_document
---

# 🧩 Debugging Challenge (30 Exercises)

Each exercise below contains **broken code**.  
Your task: **Fix the code so it performs the described action correctly.**

---

## Part 1: Basics

```{r ex1}
# Fix the code below so it prints the sum of two numbers.
a <- "4"
b <- 2
sum <- a + b
```

```{r ex2}
# Fix the code below so it performs integer division and prints the quotient.
11 / 3
```

```{r ex3}
# Fix the code below so it calculates the square root of 25.
sqroot <- sqrtx(25)
```

```{r ex4}
# Fix the code below so it evaluates to TRUE when both conditions are true.
TRUE &&| FALSE
```

---

## Part 2: Strings

```{r ex5}
# Fix the code below so it concatenates two words into one sentence.
paste("bioinfo")
```

```{r ex6}
# Fix the code below so it extracts 'HEL' from the string 'HELLO'.
substr("HELLO", 6, 10)
```

```{r ex7}
# Fix the code below so it replaces all 'A' letters with 'T'.
gsub("C", "T", "AACG")
```

```{r ex8}
# Fix the code below so it prints the variable containing the string 'R'.
name <- "R"
print(language)
```

---

## Part 3: Vectors

```{r ex9}
# Fix the code below so it calculates the mean while ignoring missing values.
nums <- c(2, NA, 4, 6)
mean(nums)
```

```{r ex10}
# Fix the code below so it prints the third element of the vector.
v <- c(10, 20, 30)
v[4]
```

```{r ex11}
# Fix the code below so it selects all numbers greater than 2.
vals <- 1:5
vals[vals > 10]
```

```{r ex12}
# Fix the code below so it generates a sequence from 1 to 10 by twos.
seq(1, 10, by = 2
```

---

## Part 4: Lists and Functions

```{r ex13}
# Fix the code below so it prints the value of 'count' from the list.
info <- list(name="A", count=5)
info[name]
```

```{r ex14}
# Fix the code below so the function adds two numbers and returns the result.
add <- function(x, y) {
  x + y
```

```{r ex15}
# Fix the code below so the function multiplies two numbers correctly.
multiply <- function(a, b) { a * b }
multiply(2)
```

```{r ex16}
# Fix the code below so the function squares the number 3.
square <- function(x) { x * x )
square(3)
```

---

## Part 5: Data Frames

```{r ex17}
# Fix the code below so the data frame is created successfully with equal column lengths.
df <- data.frame(id=1:3, val=c(5,6,7,8))
```

```{r ex18}
# Fix the code below so it selects all rows where 'val' is greater than 5.
subset(df, value > 5)
```

```{r ex19}
# Fix the code below so it adds a new column that is the log of 'val'.
df$new_col = lg(df$val)
```

```{r ex20}
# Fix the code below so it calculates the mean of column 'a' while ignoring missing values.
d <- data.frame(a=c(1,NA,3))
mean(d$a)
```

---

## Part 6: Loops and Conditions

```{r ex21}
# Fix the code below so it prints the numbers 1 to 5, one per line.
for (i in 1:5) {
print(i)
  }
```

```{r ex22}
# Fix the code below so the while loop prints numbers from 0 to 4 and then stops.
i <- 0
while (i < 5) {
  print(i)
}
```

```{r ex23}
# Fix the code below so the loop stops when i equals 5.
for (i in 1:10) {
  if (i = 5) break
}
```

---

## Part 7: Visualization

```{r ex24}
# Fix the code below so it plots 'mpg' vs 'wt' using ggplot2.
ggplot(mtcars, aes(x=mpg, y=wt)) + geom_point()
```

```{r ex25}
# Fix the code below so it correctly maps 'cyl' to the y-axis.
library(ggplot2)
ggplot(mtcars, aes(x=mpg, y=cyls)) + geom_point()
```

```{r ex26}
# Fix the code below so it draws a scatter plot using the correct geom function.
ggplot(mtcars, aes(x=mpg, y=wt)) + geompoint()
```

---

## Part 8: dplyr Analysis

```{r ex27}
# Fix the code below so it groups the data by 'cyl' and computes the mean 'mpg'.
data(mtcars)
mtcars %>% group_by(cyl) summarise(mean_mpg = mean(mpg))
```

```{r ex28}
# Fix the code below so it groups the data by the correct column name.
library(dplyr)
mtcars %>% group_by(gearz) %>% summarise(mean_mpg = mean(mpg))
```

```{r ex29}
# Fix the code below so it creates a summary column named 'mean_mpg' with the correct value.
mtcars %>% summarise(mean_mpgs = mean(mpg))
```

```{r ex30}
# Fix the code below so it correctly pipes the operations to compute the mean 'mpg' by 'cyl'.
mtcars %>%> group_by(cyl) %>% summarise(mean_mpg = mean(mpg))
```

---

# 💡 Tip
Run each chunk and read the error carefully. Modify the code until it performs the described task.
